Untitled

### 2022-03-29 Manuscript/Supplementary_Material/Indirect_interactions_trophic_guild.Rmd
Number of indirect int plot

pollinators_sp_plot <- visreg(model_freq_specif_ind, "Specificity", by="Group",line.par = list(col = 'black'),
                         strip.names=c("Bee",
                                       "Coleoptera",
                                       "Lepidoptera",
                                       "Non-bee-Hymenoptera",
                                       "Non-syrphids-diptera",
                                       "Syrphids"),gg = TRUE) + theme_bw() +
  xlab("Specialization") + ylab("Partial residuals \n for percentile")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.5))+ scale_fill_grey(start=0.5, end=0.8) +
   theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
    ggtitle("Floral visitors")

plants_sp_plot <- visreg(model_freq_specif_ind_plant, "Specificity",line.par = list(col = 'black'), by="Group",
       strip.names=c("Selfing herbs",
                     "Small outcrossing perennials",
                     "Self-incompatible perennials\nwith large flowers",
                     "Tall plants with small\nunisexual flowers",
                     "Short-lived outcrossers with\nlong zygomorphic flowers"),gg = TRUE)+ theme_bw() +
  xlab("Specialization") + ylab("Partial residuals \n for percentile")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.5))+
   theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
  ggtitle("Plants")

>>>>

pollinators_sp_plot <- visreg(model_freq_specif_ind, "Indirect_interactions", by="Group",line.par = list(col = 'black'),
                         strip.names=c("Bee",
                                       "Coleoptera",
                                       "Lepidoptera",
                                       "Non-bee-Hymenoptera",
                                       "Non-syrphids-diptera",
                                       "Syrphids"),gg = TRUE) + theme_bw() +
  xlab("Number of indirect interactions") + ylab("Partial residuals \n for percentile")+
 # scale_x_continuous(breaks = seq(0, 1, by = 0.5))+
  scale_fill_grey(start=0.5, end=0.8) +
   theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
    ggtitle("Floral visitors")

plants_sp_plot <- visreg(model_freq_specif_ind_plant, "Indirect_interactions",line.par = list(col = 'black'), by="Group",
       strip.names=c("Selfing herbs",
                     "Small outcrossing perennials",
                     "Self-incompatible perennials\nwith large flowers",
                     "Tall plants with small\nunisexual flowers",
                     "Short-lived outcrossers with\nlong zygomorphic flowers"),gg = TRUE)+ theme_bw() +
  xlab("Number of indirect interactions") + ylab("Partial residuals \n for percentile")+
  #scale_x_continuous(breaks = seq(0, 1, by = 0.5))+
   theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
  ggtitle("Plants")
